Methods to prioritise pop-up active transport infrastructure

### 2020-06-18 article.Rmd
Tweaks
Update paper abstract

<!-- This paper reports on methods developed to support the identification of pop-up active transport infrastructure. -->
In the context of reduced public transport capacity in the wake of the COVID-19 pandemic, governments are scrambling to enable walking and cycling.
A range of pop-up options exist.
The focus of this article is lane reallocation, which represents a 'quick win' for cities with roads that have a spare lane during reduced motor traffic conditions.
We found that the methods could condense the complexity of cities down to the most promising roads, which match intuition.
The evidence resulting from the methods, and future refinements, could support more evidence-based use of resources that have been made available to support implementation of pop-up schemes.

<!-- A range of pop-up options exists, including re-allocating road space, preventing through motor traffic and complete pedestrianisation of roads. -->
# RESEARCH QUESTIONS AND HYPOTHESIS

<!-- Currently the intro is 350 words, just about OK! -->

<!-- The COVID-19 pandemic has transformed all sectors of the economy, not least transport. -->
<!-- [Demand for long distance trips has plummetted](https://osf.io/preprints/socarxiv/v3g5d/) and [airline companies have gone bust](https://arxiv.org/abs/2004.08460) [@iacus_estimating_2020; @jittrapirom_exploratory_2020]. -->
Much attention has focused on the impacts of COVID-19 on long-distance travel patterns [e.g. @iacus_estimating_2020; @jittrapirom_exploratory_2020].
Yet short distance travel patterns have also changed, with a notable increase in active travel, particularly cycling, in some areas  [@harrabin_boom_2020].
The two main explanations for this are 1) the need increased need for exercise close to home during lockdowns for mental and physical health [@jimenez-pavon_physical_2020], and 2) a reduction in both public transport options and use [e.g. @tian_investigation_2020].
The second reason is particularly important given that many 'key workers' are low paid, with limited access to private automobiles.

@@

>>>>

<!-- This paper reports on methods developed to support the identification of pop-up active transport infrastructure. -->
In the context of reduced public transport capacity in the wake of the COVID-19 pandemic, governments are scrambling to enable walking and cycling.
A range of pop-up options exist.
The focus of this article is road space reallocation, which represents a 'quick win' for cities with 'spare space' along continuous road sections that have high latent cycling potential.
We developed methods to condense the complexity of city networks down to the most promising roads, producing recommendations that match intuition.
The resulting Rapid Cycleway Prioritisation Tool, deployed for all 78 transport authorities in England at the time of writing, supports evidence-based investment in pop-up and permanent schemes.

# RESEARCH QUESTIONS AND HYPOTHESIS

<!-- The COVID-19 pandemic has transformed all sectors of the economy, not least transport. -->
<!-- [Demand for long distance trips has plummetted](https://osf.io/preprints/socarxiv/v3g5d/) and [airline companies have gone bust](https://arxiv.org/abs/2004.08460) [@iacus_estimating_2020; @jittrapirom_exploratory_2020]. -->
Much attention has focused on the impacts of COVID-19 on long-distance travel patterns [e.g. @iacus_estimating_2020; @jittrapirom_exploratory_2020] but short distance travel patterns have also changed.
There has been a notable increase in active travel, particularly cycling, in some areas  [@harrabin_boom_2020].
The two main explanations for this are 1) the need increased need for exercise close to home during lockdowns for mental and physical health [@jimenez-pavon_physical_2020], and 2) a reduction in both public transport options and use [e.g. @tian_investigation_2020].
The second reason is particularly important given that many 'key workers' are low paid, with limited access to private automobiles.

@@

<!-- Todo final bit -->

<!-- - check over the responses to reviewers -->
<!-- - double check and update the paper with new images from the tool  -->
